---
output: github_document 
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw3mklinreg  

<!-- badges: start -->
[![R-CMD-check](https://github.com/mich625/HW_4/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mich625/HW_4/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/mich625/HW_4/branch/main/graph/badge.svg)](https://app.codecov.io/gh/mich625/HW_4?branch=main)
<!-- badges: end -->

# Description  
The goal of hw3mklinreg is to run a linear regression comparrable to what is found with the lm() function.

## Installation

You can install the development version of hw3mklinreg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mich625/HW_3")
```

## Example

This is a basic example which shows you how to run a regression using this package with the r base mtcars dataset. It will use mpg as the outcome based on the covariates for cylinders and weight:

```{r example}
library(hw3mklinreg)
mk_lm(Y = mtcars$mpg, X = cbind(mtcars$wt, mtcars$cyl), X_names = c("weight", "cylinders"))
```
