---
title: "mk_lm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mk_lm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
--- 

```{r, include = FALSE} 
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
The function mk_lm within the package hw3mklinreg runs a linear regression using the ordinary least squares method to calculate
the beta estimate, standard error, t statistic, and p value for the regression.  An outcome varible Y must be specified along
with a matrix X which containes the covariates.  Additionally, the names of the covariates must be put in a vector of strings
names X_names to generate the output.

```{r setup}
library(hw3mklinreg)
```

# Multiple Linear Regression 
The below shows the function running multiple linear regression from the r base mtcars package.

```{r}
mk_lm(Y = mtcars$mpg, X = cbind(mtcars$wt, mtcars$cyl), X_names = c("weight", "cylinders"))
```

To show an example from another r base dataset see below.  This dataset contains NA values.  The mk_lm function
removes all rows that contain NA's as a simplistic way to adress this potential error.
```{r}
mk_lm(Y = airquality$Ozone, X = cbind(airquality$Solar.R, airquality$Month), X_names = c("Solar Radiation", "Month"))
```


# Simple Linear Regression
This function can also do simple linear regression.  It is recommended to use an nx1 matrix still for the X covariate.

```{r}
mk_lm(Y = mtcars$mpg, X = matrix(mtcars$wt, ncol = 1), X_names = c("weight"))
```

Simple linear regression example for 2nd dataset which contains NA values is below.  

```{r}
mk_lm(Y = airquality$Ozone, X = cbind(airquality$Solar.R), X_names = c("Solar Radiation"))
```

# Comparrison to established regression function lm()
This function creates an identical output to the well established lm() function as shown below to
5 decimal spaces (multiple linear regression) 
```{r}
all.equal(round(mk_lm(Y = mtcars$mpg, X = matrix(mtcars$wt, ncol = 1), X_names = c("weight")),5)[1:12],
          round((summary(lm(formula = mpg ~ wt, data = mtcars)))$coefficients,5)[1:12])
```
Another example in the 2nd data set of the exact match to lm() proving the functions success (simple linear regression)
```{r}
all.equal(round(mk_lm(Y = airquality$Ozone, X = cbind(airquality$Solar.R), X_names = c("Solar Radiation")),5)[1:8],
          round((summary(lm(formula = Ozone ~ Solar.R, data = airquality)))$coefficients,5)[1:8])
```
# Benchmarking
When testing efficiency, the mk_lm is substantially faster than lm.  This is expected with proper development due to the fact that the lm function has some additional processes then the mk_lm function does not do.

```{r}
bench::mark(round(mk_lm(Y = mtcars$mpg, X = matrix(mtcars$wt, ncol = 1), X_names = c("weight")),5)[1:12],round((summary(lm(formula = mpg ~ wt, data = mtcars)))$coefficients,5)[1:12], iterations = 1000 )
```
Benchmarking for simple linear regression is shown here too

```{r}
bench::mark(round(mk_lm(Y = airquality$Ozone, X = cbind(airquality$Solar.R), X_names = c("Solar Radiation")),5)[1:8],
          round((summary(lm(formula = Ozone ~ Solar.R, data = airquality)))$coefficients,5)[1:8], iterations = 1000)
```
